Non-word repetition in Yélî Dnye

### 2020-09-14 manuscript.Rmd
add comment for AC to rmd

#quick fix, but should be fixed upstream @ac
trnsc$Sex[trnsc$Sex=="F"]<-"G"
trnsc$Sex=factor(trnsc$Sex)
trnsc$birthOrder=as.numeric(trnsc$birthOrder)
```

>>>>

#quick fix, but should be fixed upstream @ac
# M2A: Seems like you already did this, and the line below
# is setting the is.na(trnsc$Sex) cases to "G" -- I assume
# that's not a desirable outcome so am commenting it out
# trnsc$Sex[trnsc$Sex=="F"]<-"G"
trnsc$Sex=factor(trnsc$Sex)
trnsc$birthOrder=as.numeric(trnsc$birthOrder)
```
